### 2017-09-19 icde/sec-exp.tex

\newcommand{\graphscale}{0.36} %0.38
\newcommand{\graphmargin}{-4ex}
\newcommand{\exppath}{./exp/}
%\newcommand{\exppath}{./exp/wpr/}
%%% all in 1 Figure
\begin{figure*}[tb!]
%\vspace{-2ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
%\hspace{10ex}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-futureyear}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-t}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-fcdiff}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-sigma}
\includegraphics[scale=\graphscale]{./exp/AAN_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-lambda}
\includegraphics[scale=\graphscale]{./exp/AAN_lambda.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-futureyear}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-t}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-fcdiff}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-sigma}
\includegraphics[scale=\graphscale]{./exp/AMiner_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-lambda}
\includegraphics[scale=\graphscale]{./exp/AMiner_lambda.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-futureyear}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-t}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-fcdiff}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-sigma}
\includegraphics[scale=\graphscale]{./exp/MAG_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-lambda}
\includegraphics[scale=\graphscale]{./exp/MAG_lambda.eps}}
\end{center}
\vspace{-2.5ex}
\caption{\small Accuracy tests with \fcita (all) and \recom ((d)--(e), (i)--(j) and (n)--(o))}
\label{exp-pairacc}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
%\hspace{10ex}
\subfigure[{\scriptsize TWPageRank (batch vs. inc.)}]{\label{exp-aminer-time1}
\includegraphics[scale=\graphscale]{./exp/AMiner_time_twpr.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize Comparison of ranking algorithms}]{\label{exp-aminer-time2}
\includegraphics[scale=\graphscale]{./exp/AMiner_time.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize TWPageRank (batch vs. inc.)}]{\label{exp-mag-time1}
\includegraphics[scale=\graphscale]{./exp/MAG_time_twpr.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize Comparison of ranking algorithms}]{\label{exp-mag-time2}
\includegraphics[scale=\graphscale]{./exp/MAG_time.eps}}
\end{center}
\vspace{-2ex}
\caption{\small Efficiency tests on \aminer ((a)--(b)) and  \magdata ((c)--(d))}
\label{exp-time}
\vspace{-3ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\graphscaleexpapp}{0.25}
\newcommand{\graphmarginexpapp}{-2ex}
%%% all in 1 Figure
\begin{figure*}[tb!]
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-recm.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-recm.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-recm.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2ex}
%\hspace{-10ex}
\subfigure[{\scriptsize \aan  with \fcita}]{\label{exp-aan-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-fcita.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-fcita.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-fcita.eps}}
\end{center}
\vspace{-2ex}
\caption{\small Accuracy tests: varying aggregating parameters $\alpha$ and $\beta$}
\label{exp-ab}
\vspace{-3ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-recom-drank}
\includegraphics[scale=0.35]{./exp/AAN_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-recom-drank}
\includegraphics[scale=0.35]{./exp/AMiner_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-recom-drank}
\includegraphics[scale=0.35]{./exp/MAG_TWPageRank_recom.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \aan with \fcita}]{\label{exp-aan-fcita-drank}
\includegraphics[scale=0.35]{./exp/AAN_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-fcita-drank}
\includegraphics[scale=0.35]{./exp/AMiner_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-fcita-drank}
\includegraphics[scale=0.35]{./exp/MAG_TWPageRank_fcita.eps}}
\end{center}
\vspace{-2ex}
\caption{\small Impacts of the TWPageRank on accuracy: varying importance weighting
factor $\lambda$}
\label{exp-drank}
\vspace{-3ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\etitle{Exp-4.4}.
\marked{To evaluate the impacts of our TWPageRank, we compared our \ensemblerank with \drank, an alternative of \ensemblerank by removing the peak time in  Eq.~(\ref{eq-infl-weights}) of  TWPageRank, \ie $w(u,v)=e^{\sigma(T_u-T_v)}$. % with a directly exponentially decayed impact weights without peak times, \ie , .
%The two algorithms produce the same popularity while different prestige.
To better understand the impacts, we varied the importance weighting factor $\lambda$ from 0.1 to 1. Note that the ranking results are the same when $\lambda=0$ due to the same popularity computation. The results are reported in Fig.~\ref{exp-drank}, where the numbers represent the improvement of \PairAcc by \ensemblerank over the one by \drank.}

>>>>

\newcommand{\graphscale}{0.36} %0.38
\newcommand{\graphmargin}{-4ex}
\newcommand{\exppath}{./exp/}
%\newcommand{\exppath}{./exp/wpr/}
%%% all in 1 Figure
\begin{figure*}[tb!]
%\vspace{-2ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
%\hspace{10ex}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-futureyear}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-t}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-fcdiff}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-sigma}
\includegraphics[scale=\graphscale]{./exp/AAN_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-lambda}
\includegraphics[scale=\graphscale]{./exp/AAN_lambda.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-futureyear}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-t}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-fcdiff}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-sigma}
\includegraphics[scale=\graphscale]{./exp/AMiner_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-lambda}
\includegraphics[scale=\graphscale]{./exp/AMiner_lambda.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-futureyear}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-t}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-fcdiff}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-sigma}
\includegraphics[scale=\graphscale]{./exp/MAG_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-lambda}
\includegraphics[scale=\graphscale]{./exp/MAG_lambda.eps}}
\end{center}
\vspace{-2.5ex}
\caption{\small Accuracy tests with \fcita (all) and \recom ((d)--(e), (i)--(j) and (n)--(o))}
\label{exp-pairacc}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
%\hspace{10ex}
\subfigure[{\scriptsize TWPageRank (batch vs. inc.)}]{\label{exp-aminer-time1}
\includegraphics[scale=\graphscale]{./exp/AMiner_time_twpr.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize Comparison of ranking algorithms}]{\label{exp-aminer-time2}
\includegraphics[scale=\graphscale]{./exp/AMiner_time.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize TWPageRank (batch vs. inc.)}]{\label{exp-mag-time1}
\includegraphics[scale=\graphscale]{./exp/MAG_time_twpr.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize Comparison of ranking algorithms}]{\label{exp-mag-time2}
\includegraphics[scale=\graphscale]{./exp/MAG_time.eps}}
\end{center}
\vspace{-2ex}
\caption{\small Efficiency tests on \aminer ((a)--(b)) and  \magdata ((c)--(d))}
\label{exp-time}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\graphscaleexpapp}{0.25}
\newcommand{\graphmarginexpapp}{-2ex}
%%% all in 1 Figure
\begin{figure*}[tb!]
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-recm.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-recm.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-recm.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2ex}
%\hspace{-10ex}
\subfigure[{\scriptsize \aan  with \fcita}]{\label{exp-aan-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-fcita.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-fcita.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-fcita.eps}}
\end{center}
\vspace{-2ex}
\caption{\small Accuracy tests: varying aggregating parameters $\alpha$ and $\beta$}
\label{exp-ab}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-recom-drank}
\includegraphics[scale=0.35]{./exp/AAN_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-recom-drank}
\includegraphics[scale=0.35]{./exp/AMiner_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-recom-drank}
\includegraphics[scale=0.35]{./exp/MAG_TWPageRank_recom.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \aan with \fcita}]{\label{exp-aan-fcita-drank}
\includegraphics[scale=0.35]{./exp/AAN_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-fcita-drank}
\includegraphics[scale=0.35]{./exp/AMiner_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-fcita-drank}
\includegraphics[scale=0.35]{./exp/MAG_TWPageRank_fcita.eps}}
\end{center}
\vspace{-2ex}
\caption{\small Impacts of the TWPageRank on accuracy: varying importance weighting
factor $\lambda$}
\label{exp-drank}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\etitle{Exp-4.4}.
To evaluate the impacts of our TWPageRank, we compared our \ensemblerank with \drank, an alternative of \ensemblerank by removing the peak time in  Eq.~(\ref{eq-infl-weights}) of  TWPageRank, \ie $w(u,v)=e^{\sigma(T_u-T_v)}$. % with a directly exponentially decayed impact weights without peak times, \ie , .
%The two algorithms produce the same popularity while different prestige.
To better understand the impacts, we varied the importance weighting factor $\lambda$ from 0.1 to 1. Note that the ranking results are the same when $\lambda=0$ due to the same popularity computation. The results are reported in Fig.~\ref{exp-drank}, where the numbers represent the improvement of \PairAcc by \ensemblerank over the one by \drank.
